A graph-based data model for interactive evolutionary computation

### 2017-01-19 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Framework described

\begin{itemize}
  \item { \tt Interactive Evolutionary Computational system.}  
  This is the real world system that we are going to model, it consist of
  human users and their interactions with one or more individuals from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm.
  There is also the posibility that fitness is or part of the search is done
  in devices lended by the human. The information gathered through the 
  interaction will guide the search.

% We could reference Nod

  \item {\tt IEC Graph}
  This is the model proposed in this work: A graph database modeling
  the IEC system. The  main components are the social network of users and the population. This database is the back-end of the system, is used by the EA and
  the user interface.

  \item {\tt Evolutionary Algorithm} 
  This algorithm queries the graph model, and then updates those nodes that 
  are part of the population. 
\end{itemize}

@@

\subsection{IEC Graph Model}

>>>>

\begin{itemize}
  \item { \tt Interactive Evolutionary Computational system.}  
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the posibility that fitness or even part of the search 
  to be done by devices lended by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item {\tt IEC Data Model}
  A data model is used to describe the IEC system prior to a physical 
  implementation. 
  %% This block is maybe not needed but in our ES-I implementation
  %% we use Relational (PosgreSQL), Objects (JSON-Redis) and Graphs (Neo4J)
  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a Class Digram for a 
  key-value store. 
  %%
  %%
  A graph is proposed for modelling the social network
  of users and their interaction with the population. This database 
  is the back-end of the system, is used by the EA and the user interface.

  \item {\tt Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physicaly created
  the new population.  
\end{itemize}

@@

\subsection{IEC Graph Conceptual Model}
